Foraging: The Triumphant Return

### 2022-06-06 manuscript.tex

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusion: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

@@

Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}. In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run. However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022}. By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu2020}.

@@

\subsubsection{Clarke et al 2022}

\subsubsection{Ppric et al}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Foraging refers to search involving multiple targets or multiple types of targets, and as a model task has a long history in animal behaviour and human cognition research. Foraging behaviour is usually operationalized using summary statistics, such as average distance covered during target collection (the path length) and the frequency of switching between target types. We recently introduced an alternative approach, which is to model each instance of target selection as random selection without replacement. Our model produces estimates of a set of foraging biases, such as a bias to select closer targets or targets of a particular category. Here we apply this model to predict individual target selection events. We add a new start position bias to the model, and generate foraging paths using the parameters estimated from individual participants’ pre-existing data. The model predicts which target the participant will select next with a range of accuracy from 43\% to 69\% across participants (chance is 11\%). The model therefore explains a substantial proportion of foraging behaviour in this paradigm. The situations where the model makes errors reveal useful information to guide future research on those aspects of foraging that we have not yet explained.}

% Keywords
\keyword{foraging; visual search; bayesian model; decision; strategy (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

@@

Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}. Foraging engages a wide range of different perceptual, cognitive, and decision-related skills, and is an ecologically relevant behaviour for most species, including humans. For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets. For example, the classic marginal value theorem \cite {charnov1976} is generally good at predicting when an organism will decide to stop searching in a patch and move on to another, based on the finding rate dropping below an expected rate, and taking into account the relative energy costs of traveling between patches versus staying within a patch. There has also been a concerted effort to characterize the spatial patterns of foraging behaviour. The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g. \citep {bartumeus2005}, but see also \citep{benhamou2007}).

Another general principle of foraging is that of the “search image”, which describes the perceptual features that a foraging animal can use to identify targets or classes of targets \cite{Dukas1993}. A limited capacity for complex search images means that dividing attention over more than one kind of potential search target can impede search, particularly when what distinguished targets from distractors is not a simple feature like colour or motion. As a result, foragers tend to search in “runs” of one type of target before switching to another. In humans, this behaviour has been studied using computer-based displays of targets and distractors (e.g. \citep{ kristjansson2014}), in which participants must “collect” targets (by clicking or tapping on them) and ignore distractors. When targets can be identified based on a single, easily distinguishable feature (for example, find all the red and green shapes and ignore the blue and yellow shapes) participants tend to switch frequently between different types of targets, taking a relatively efficient path through the array. In contrast, when targets are defined based on a combination of more than one feature (e.g. find all the red squares and green circles and ignore the red circles and green squares), participants tend to switch far less frequently, often selecting all the targets of one category and then all the targets of the other. Consequently, the path taken to collect the targets is less efficient. In other words, frequent switching between target types limits the distance travelled between targets, while collecting all the targets of each type before switching to the other type sacrifices some efficiency of movement in service of reducing the mental workload.

Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately. In many cases, the pattern of foraging behaviour has also been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run. However, we have recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022}. By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu2020}.

@@
